Diversification of Australian blind snakes

### 2022-11-18 manuscript.Rmd
biome transitions

Following the hypothesized colonisation event from a single common ancestor, the diversifcation of _Anilios_ occurred very rapidly. Descendents of the earliest split remained in the tropical grassland biome but within a million years later another split occured. The earliest biome transition was from tropical grassland biome into the temperate forest biome around 25 MYA (95% HPD: 28 – 22 MYA) for branch leading _A. siliva_, and another branch that included current arid and mediterranean species starting 24 MYA (95% HPD: 28 – 21 MYA). Based on 50 biogeographic stochastic mapping, we found that the largest source of total outward dispersal (anagenetic and cladogenetic) is the tropical grassland biome (642 dispersals, mean = 71.3 per BSM) almost double the number of dispersals from the arid biome (395 dispersals, mean = 43.9 per BSM) (\@ref(fig:fig-biogeobears)).

>>>>

Following the hypothesized colonisation event from a single common ancestor, the diversifcation of _Anilios_ occurred very rapidly. Descendents of the earliest split remained in the tropical grassland biome but within a million years later another split occured. The earliest biome transition was from tropical grassland biome into the temperate forest biome around 25 MYA (95% HPD: 28 – 22 MYA) for branch leading _A. siliva_, and another branch that included current arid and mediterranean species starting 24 MYA (95% HPD: 28 – 21 MYA). Based on 50 biogeographic stochastic mapping, we found that the largest source of total outward dispersal (anagenetic and cladogenetic) is the tropical grassland biome (mean = XX) almost double the number of dispersals from the arid biome (mean = XX) (\@ref(fig:fig-biogeobears)). On the other hand, the largest sink for all inward dispersal is the mediterranean biome (
